\subsubsection{Merge Sort}
The merge sort algorithm is a divide and conquer sorting algorithm. The algorithm works by splitting the array into many smaller arrays, sorting the smaller arrays and then merging them back together into a sorted version of the original array. This project contains an implementation which splits the array recursivly until a given limit is hit, or the array size is 1. If the limit is given, the array will be sorted using insertion sort, before merging.
\par
While performing the sort, every stage of the algorithm will be saved in a list of steps. There are three stages which will be stored as a step.
\begin{itemize}
    \item Initial. The initial step is stored before the sorting starts. It contains a copy of the unsorted array and a reference to the limit.
    \item Split. The split step is added when an array is split into two arrays. It contains a copy of the array being split, and copies of the new arrays.
    \item Merge. The merge step is added after two arrays have been merged to a new array containing the sorted version of all the elements. It contains a copy of the two arrays being merged, and a copy of the resulting array.
\end{itemize}
\par
When implementing the algorithm, performance and memory usage were not considered to be important. The algorithm will only run once per question to generate the steps so that each student's answer can be compared to the right way to perform a merge sort. For this reason, the intermediate arrays are allocated dynamically instead of being reused in later steps. This gives the algorithm worse performance, but it's average case performace is still O(n * logn). Memory usage has not been considered because the algorithm has to store more information than normal to store the steps.