\subsection{Shell Sort}
Shell sort is an sorting algorithm that is based of insertion sort. The key difference between the two sorting algorithm is in performance. Shell sort will have both an average case and a worst case of O(n) runtime. The main reason for this is that shell sort will sort entries in the list that are at certain intervals from each other. The algorithm is essentially dividing list entries into smaller sublists in order to make the sorting more efficient. Through this method shell sort avoids having to check every entry in the list, which allows the algorithm to remove main drawback of using insertion sort.
\\[11pt]
The starting interval used in a shell sort is usually based on approximately half length of the list. The algorithm uses the interval to divide up the entries in the list. The entries chosen together are then compared to each other and sorted based on their value. Once the list has been effectively sorted the list on the current interval, the interval's value is halved and the sorting process starts anew. Eventually the interval will reach a value of 1, which is essentially will cause shell sort to finish sorting the list using insertion sort algorithm. Of course since the list should at this point be almost completely sorted, and therefore the insertion sort should never achieve a runtime of $O^2$.
\\[11pt]
The implementations of shell sort used in this project is currently not the best implementation of shell sort. The implementation used is heavily inspired by practical shell sort methods taught during algorithms and data structures courses. This method is even more alike the insertion sort algorithm then it needs to be. However the shell short used in this project should end up with the same result after each interval sort, which is important considering most exercises involving shell sort focuses on students finding the result after each k-sort.\cite{ShellSort:Geeks}  