\subsubsection{Vuex}
One problem that one can run into when creating a medium to large size application in Vue, is how to handle variables used by more than one component. This is solved by a package called vuex\cite{VUEX}, which lets us store variables in one location and all components can get and change it. The vuex package is used as a store for variables for all Vue components. When creating a store it will be possible to split it up into smaller stores and still have all components be able to access the entire store. A store will mostly consist of a state, mutations, actions and getters. The state is where all the variables will be stored. If you want to get a variable this will happen in the getters object which will contain functions that will have access to the state. Getters can't change the state, only get variables. If you want to change a variable, you will have to mutate the state. This will be done in two steps. The first step is to call a action function. This will have buisness logic where you will have read access to the state. Here you will for the most part check that the variable you are getting is of the correct format, or getting a varibale from the state and changing it. The second step is to call the mutation function from the action function with the change you want. The mutation function will have write access to the state and it will be here the state actually changes. The getters and actions will be accessible from all components in the Vue project. This is a package that is needed for variables that are used in multiple Vue components. It also allows the variables to be mutated in predictable way, making sure that you don't get an unexpected state.