\subsubsection{GraphDrawer}
If new question types are implemented which require the GraphDrawer to keep track of thousands of nodes at the same time, there might be performance issues on some systems. The nodes are currently stored in an array. This means that if the array is searched for a node on the screen, all of the nodes need to be checked, even those on the opposite side of the world. Many operations starting on one node, and ending at a node close to the first node (e.g., selecting nodes by dragging the mouse) would be more performant if a spatial data structure\cite{SpatialDatastructure} was used instead.
\\[11pt]
The current system is designed to work with both touch screens and cursors. Because of this, two choices were made to make the development simpler and less time-consuming.
\begin{enumerate}
    \item When a user needs to enter text or numbers, the JavaScript alert popup is used because this works in all browsers. Some users with a keyboard would have been able to write faster if the GraphDrawer read the input directly. Mobile browsers do not allow a website to open the virtual keyboard from a script. If the mobile browsers change this in the future, a different method for retrieving the user input could be used. Some browsers allow the user to block popups. If this is done, the user can no longer enter text.
    \item For simplicity both desktop and mobile users control the GraphDrawer the same way. User testing can be done to find the gestures which feel the most natural. If the natural way to do something is different depending on the system, different handlers can be implemented.
\end{enumerate}
Every time the world state changes, the canvas is redrawn. Changes outside the camera view should not make the GraphDrawer redraw the world. If only a small part of the world inside the camera view is changed, only that part needs to be redrawn. This has not been implemented because there have not been any performance issues with the current question types.