\subsubsection{To add a question:}
\begin{userManualItemlist}
    \item[Step I.] Navigate to the questions page.
    \item[Step II.] Click the "+" button.
    \item[Step III.] Enter the question information in the title and description fields.
    \item[Step IV.] If you want a timed question, select the time with the slider or the input field.
    \item[Step V.] If you want to add media to a question:
    \begin{enumerate}
        \item Click "Media".
        \item Select what type of media you want to include.
        \item If you are adding images, click the "Choose a file to upload..." button. This will open a file browser where you can select the images.
        \item If you added an image by mistake, it can be removed by clicking the "Delete" button.
        \item If you are adding a graph, use the GraphDrawer tool to create it.
        \item When you are done, click the "Add canvas as image" button.
        \item If you are adding a table, use the add and remove buttons to create the table.
        \item Click on table cells to enter the value.
        \item When you are done, click the "Add table" button.
    \end{enumerate}
    \item[Step VI.] Click "Solution type".
    \item[Step VII.] Select the solution type from the select element.
    \item[Step VIII.] Follow the instructions on the screen to enter the required information.
    \item[Step IX.] Click the "Add" button. 
\end{userManualItemlist}

\subsubsection{To edit a question:}
\begin{userManualItemlist}
    \item[Step I.] Navigate to the questions page.
    \item[Step II.] Click the edit button.
    \item[Step III.] Edit the information.
    \item[Step IV.] Click the "Add" button.  
\end{userManualItemlist}
